Interpolants and Error Bounds for Modeling and Predicting Variability in Computer Systems

### 2020-07-28 3-Disseration/strong.tex
Updated thesis document, sent draft to Dr. Watson.

\begin{figure}[htb]
  \centering
  \begin{tikzpicture}
    \node (img)  {\includegraphics[width=0.75\textwidth,]{Figures/NA/Fig1.pdf}};
    \node[below=of img, node distance=1cm, yshift=1cm] {I/O Throughput};
    \node[left=of img, node distance=0cm, rotate=90, anchor=center,yshift=-0.7cm] {CDF Value};
  \end{tikzpicture}
  \vspace{-0.3cm}
  \caption{In this HPC I/O example, the general methodology for
    predicting a CDF and evaluating error can be seen. The Delaunay
    method chose three source distributions (dotted lines) and
    assigned weights \{.3, .4, .3\} (top to bottom at arrow). The
    weighted sum of the three known CDFs produces the predicted CDF
    (dashed line). The KS Statistic (arrow) computed between the true
    CDF (solid line) and predicted CDF (dashed line) is 0.2 for this
    example. The KS test null hypothesis is rejected at $p$-value
    0.01, however it is not rejected at $p$-value 0.001.}
  \label{fig:prediction-example}
\end{figure}

@@

A hurdle when modeling function-valued outputs such as cumulative
distribution functions (CDFs) or probability density functions (PDFs)
is that certain properties must be maintained. It is necessary that a
PDF $f: \mathbb{R} \rightarrow \mathbb{R}$ have the properties $f(x)
\geq 0$ and $\int_{-\infty}^{\infty}f(x)dx = 1$. However, for a CDF
$F: \mathbb{R} \rightarrow \mathbb{R}$ the properties are
$F(x) \in [0,1]$ and $F(x)$ is absolutely continuous and
nondecreasing. This work utilizes the fact that a convex combination
of CDFs (or PDFs) results in a valid CDF (or PDF). Given $G(x) =
\sum_{i}w_i F_i(x)$, $\sum_{i} w_i = 1$, $w_i \geq 0$, and each $F_i$
is a valid CDF, $G$ must also be a valid CDF. A demonstration of how
this is applied can be seen in Figure \ref{fig:prediction-example}.

@@

The two-sample KS test is a useful nonparametric test for comparing
two CDFs while only assuming stationarity, finite mean, and finite
variance. The null hypothesis (that two CDFs come from the same
underlying distribution) is rejected at level $p \in [0,1]$ when
 $$ KS > \sqrt{-\frac{1}{2}\ln\biggl(\frac{p}{2}\biggr)} \sqrt{\frac{1}{n_1} + \frac{1}{n_2}}, $$
with distribution sample sizes $n_1,n_2 \in \mathcal{N}$. For all
applications of the KS test presented in this work $n_1 = n_2$. An
example of the round-trip prediction methodology from known and
predicted distributions to the calculation of error can be seen in
Figure \ref{fig:prediction-example}.

\subsection{Feature Weighting}
\label{sec:feature_weighting}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth,]{Figures/NA/example_distribution_prediction.pdf}
  \caption{In this HPC I/O example, the general methodology for
    predicting a CDF and evaluating error can be seen, where M means
    $\times 10^6$. The Delaunay method chose three source
    distributions (dotted lines) and assigned weights \{.1, .3, .6\}
    (top to bottom at middle). The weighted sum of the three known
    CDFs produces the predicted CDF (dashed line). The KS Statistic
    (vertical line) computed between the true CDF (solid line) and
    predicted CDF (dashed line) is 0.2 for this example. For this
    example the KS test null hypothesis is rejected at $p$-value 0.01,
    however it is not rejected at $p$-value 0.001.
  \vspace{-.1cm}}
  \label{fig:prediction-example}
\end{figure}

@@

A hurdle when modeling function-valued outputs such as cumulative
distribution functions (CDFs) or probability density functions (PDFs)
is that certain properties must be maintained. It is necessary that a
PDF $f: \mathbb{R} \rightarrow \mathbb{R}$ have the properties $f(x)
\geq 0$ and $\int_{-\infty}^{\infty}f(x)dx = 1$. Instead, for a CDF
$F: \mathbb{R} \rightarrow \mathbb{R}$ the properties are
$F(x) \in [0,1]$ and $F(x)$ is absolutely continuous and
nondecreasing. This work utilizes the fact that a convex combination
of CDFs (or PDFs) results in a valid CDF (or PDF). Given $G(x) =
\sum_{i}w_i F_i(x)$, $\sum_{i} w_i = 1$, $w_i \geq 0$, and each $F_i$
is a valid CDF, $G$ must also be a valid CDF. A demonstration of how
this is applied can be seen in Figure \ref{fig:prediction-example}. 
In this example the KS test null hypothesis is rejected at $p$-value
0.01, however it is not rejected at $p$-value 0.001.

@@

The two-sample KS test is a useful nonparametric test for comparing
two empirical CDFs while only assuming stationarity,
finite mean, and finite variance. The null hypothesis (that two
empirical CDFs come from the same underlying distribution)
is rejected at level $p \in [0,1]$ when
 $$ KS > \sqrt{-\frac{1}{2}\ln\biggl(\frac{p}{2}\biggr)}
\sqrt{\frac{1}{n_1} + \frac{1}{n_2}}, $$ with distribution sample
sizes $n_1,n_2 \in \mathcal{N}$. For all applications of the KS test
presented in this work $n_1 = n_2$. An example of the process of
generating predicted distributions from known distributions and the
subsequent calculation of error can be seen in Figure
\ref{fig:prediction-example}. A brief listing of relevant statistical
terms used throughout this work is provided in the Appendix (Section
\ref{sec:appendix}).

%% ===================================================================
\subsection{Feature Weighting}
\label{sec:feature_weighting}
